Tropical Andes plant species BIEN data

### 2023-08-02 code/L0/L0_TropicalAndes_plants_BIEN_occ.Rmd
add combine occ by country code
load forest shape unsuccessfully get occurrence data from BIEN

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(dplyr)
```

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ_ec <- BIEN_occurrence_country(country = "Ecuador", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_ve <- BIEN_occurrence_country(country = "Venezuela", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_pe <- BIEN_occurrence_country(country = "Peru", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_co <- BIEN_occurrence_country(country = "Colombia", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)

TropicalAndes_BIEN_occ_bo <- BIEN_occurrence_country(country = "Bolivia", all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)
```

```{r}
# combine occ

```

>>>>

# Load required packages
```{r}
library(BIEN)
library(tidyr)
library(dplyr)
library(sf)
```

# Load Tropical Andes moist lowland and montane forest shape
```{r}
TropicalAndes_IUCNHabitat_Forest <- st_read(file.path(data_path, "TropicalAndes_IUCNHabitat_Forest.shp"))
```

# Get occurrence data for Tropical Andes from BIEN database
```{r}
TropicalAndes_BIEN_occ <- BIEN_occurrence_sf(TropicalAndes_IUCNHabitat_Forest, all.taxonomy = TRUE, observation.type = TRUE, political.boundaries = TRUE, collection.info = TRUE)
```
